---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# leagueCR7

<!-- badges: start -->
<!-- badges: end -->

The goal of leagueCR7 is to make available 110938 league matches across the world between the period of 2018 and 2022 

## Installation

You can install the development version of leagueCR7 from GitHub remotes::install_github("Franosei/Football_dataset_package/leagueCR7")

To avoid installing the package from Github, you can use use the following command in your console
"renv::restore()"

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(leagueCR7)
library(dplyr)
library(ggplot2)
library(reshape2)
```

```{r}
summary(leagueCR7)
```


```{r,fig.width = 15,fig.height = 10}
mydata <- leagueCR7::leagueCR7[, c(1,5:13)]
cormat <- round(x = cor(mydata), digits = 2)
melted_cormat <- melt(cormat)
melted_cormat %>% 
  ggplot(aes(x=Var1, y=Var2, fill=value)) + 
  geom_tile(colour = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "pink", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation")+
  scale_x_discrete(label=abbreviate)+
  scale_y_discrete(label=abbreviate)+
  theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),axis.text.x = element_text(angle = 45, hjust=1))+
  labs(caption = "figure 3: Heatmap (correlation plot)")+
  theme(plot.caption = element_text(hjust = 0.5)
  )+
  geom_text(aes(Var2, Var1, label = value), color = "black", size = 3,alpha=2 )+
  theme(text = element_text(size=20))

```

